Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-12 paper.qmd
Updated with new functions

ar <- umap_scurve |>
  summarise_at(c("UMAP1", "UMAP2"), 
    function(x) max(x)-min(x)) |>
  mutate(ar = UMAP2/UMAP1) |>
  pull(ar) # This is a bit cumbersome too
hr <- 2/sqrt(3)
umap_scurve_scaled <- umap_scurve |>
  mutate_at(c("UMAP1", "UMAP2"), 
    function(x) (x - min(x))/(max(x)-min(x))) |> # can be no missings
  mutate(UMAP2 = UMAP2 * ceiling(ar/hr) * hr)

@@

hb_obj_scurve <- hex_binning(data = umap_scurve_scaled, x = "UMAP1", 
                      y = "UMAP2", num_bins_x = num_bins_x_scurve, 
                      num_bins_y = num_bins_y_scurve, x_start = NA, y_start = NA, 
                      buffer_x = NA, buffer_y = NA, hex_size = hex_size_scurve, 
                      col_start = "UMAP")

## Data set with all possible centroids in the hexagonal grid
all_centroids_df <- as.data.frame(do.call(cbind, hb_obj_scurve$centroids))

## Generate all coordinates of hexagons
hex_grid <- as.data.frame(do.call(cbind, hb_obj_scurve$hex_poly))

## To obtain the standardise counts within hexbins
counts_df <- as.data.frame(do.call(cbind, hb_obj_scurve$std_cts))
df_bin_centroids <- extract_hexbin_centroids(centroids_df = all_centroids_df, 
                                             counts_df = counts_df)

>>>>

umap_scurve_scaled <- gen_scaled_data(data = umap_scurve, x = "UMAP1", 
                                      y = "UMAP2", hr = 2/sqrt(3))

# ar <- umap_scurve |>
#   summarise_at(c("UMAP1", "UMAP2"), 
#     function(x) max(x)-min(x)) |>
#   mutate(ar = UMAP2/UMAP1) |>
#   pull(ar) # This is a bit cumbersome too
# hr <- 2/sqrt(3)
# umap_scurve_scaled <- umap_scurve |>
#   mutate_at(c("UMAP1", "UMAP2"), 
#     function(x) (x - min(x))/(max(x)-min(x))) |> # can be no missings
#   mutate(UMAP2 = UMAP2 * ceiling(ar/hr) * hr)

@@

hb_obj_scurve <- hex_binning(data = umap_scurve_scaled, x = "UMAP1", 
                      y = "UMAP2", num_bins_x = num_bins_x_scurve, 
                      num_bins_y = num_bins_y_scurve, x_start = NA, y_start = NA, 
                      buffer_x = 0.346, buffer_y = 0.3, hex_size = hex_size_scurve, 
                      col_start = "UMAP")

## Data set with all possible centroids in the hexagonal grid
all_centroids_df <- hb_obj_scurve$centroids

## Generate all coordinates of hexagons
hex_grid <- hb_obj_scurve$hex_poly

## To obtain the standardise counts within hexbins
counts_df <- hb_obj_scurve$std_cts
df_bin_centroids <- extract_hexbin_centroids(centroids_df = all_centroids_df, 
                                             counts_df = counts_df)
